---
title: "DATA607Hwk3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(stringr)

```


Load raw data
```{r}
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
```


Extract all names
```{r}
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}")) 
name
```


Rearrange vector to First Name then Last Name
```{r}
name
fl_extract <- unlist(str_split(name[5], ","))
fl_extract
new_name <- str_c(fl_extract[2], fl_extract[1], sep = " ")
new_name
name[5] <- new_name
fl_extract <- unlist(str_split(name[2], ","))
fl_extract
new_name <- str_c(fl_extract[2], fl_extract[1], sep = " ")
new_name
name[2] <- new_name
```


show all new names
```{r}
name
```


Vector indicating if charachter has a title
```{r}
pmatch(c("Dr.", "Rev."), name)
```


Vector checking if character has a second name
```{r}
str_extract(name, "[[:alpha:]][[:blank:]][[:alpha:]]")
```


Question 4 - describe type of strings and construct example
4.1 Digits at the end of the exression or sting ex: Street number 87
```{r}
#[0-9]+\\$
```


4.2 Word edge, all letters a-z, item should be matched at least 1 time but no more than 4, follwed by word edge. Or a 4 letter word. ex: "book"
```{r}
#\\b[a-z]{1,4}\\b
```


4.3 Can contain a "." and is optional. Sting or expression ends in .txt ex: "file.txt"
```{r}
#.*?\\.txt$
```


4.4 2 digits, a forward slash, followed by 2 more digits, a forward slash, and ends with 4 digits. Like a date ex: 02/01/2018
```{r}
#\\d{2}/\\d{2}/\\d{4}
```


4.5 Optional period(s) enclosed in perentheses, followed by another optional period(s), followed by a forward slash and ending with the number 1. ex: (..)../1 or ()../1 or (..)/1
```{r}
#<(.+?)>.+?</\\1>
```

